Standardized crypto-loans on\\ the Cardano blockchain

### 2021-02-03 papers/actus2021/article.tex
revised section 2. Some questions to answer: beginning % SJT ...

@@

\noindent
The \emph{spread} parameter here loosely represents the difference between
the average prime 
% SJT explain "prime" here.
rate that the lender expects (the benchmark yield) and
the rate imposed by the driver - the higher the spread, the higher
the resulting interest rate. The multiplier %effectively 
rescales the interest rate value 
% SJT used value here rather than plot: is that OK?
in order to represent the changes to be made converting between different units
of measurement: how many percentage points you would get for a usd-to-kilowatt conversion
and so on.

In the context of ACTUS and other event-based frameworks, there is
one more factor influencing interest rates thorough scaling:

\noindent 
\begin{equation}
interestPayment=interestScalingFactor*interestRate*notional
\end{equation}

This scaling is dynamic and loosely adjusts for variance (volatility)
of the asset that the interest rate driver represents.

@@

Counterparty might decide to reinvest profit received as interest
from the same loan. In the simplest case, this renders as compound
interest. This can be modelled through interest accrual and capitalisation,
for instance contracts from the ACTUS specification accrue interest
between interest payments and can transfer interest to a notional
during interest capitalisation event (IPCL).

Overall, variable interest rates introduce a certain risk for a lender,
thus they are subject to hedging. While any instrument that depends
on the same risk factor (interest rate driver) would suffice - the
most popular way to hedge a variable interest rate loan is interest
rate swap. This instrument allows two (or more) parties to exchange
their incomes - one from fixed interest rate loans, the other one
- from variable interest

@@

Trustless setups, especially ones in the cryptocurrency world (e.g.
decentralised smart-contracts and exchanges) require zero trust between
party and counterparty involved in a contract. In case of a loan,
this literally means that counterparty has zero-obligation to pay
the money back, thus rendering the loan useless for a party. Such
risks are usually addressed by introducing collaterals: 
\begin{enumerate}
\item Alice would like to borrow 1000 USD 
\item She has Bitcoin assets cost around 1500 USD, which she intends to
hold throughout a year, so Alice has high confidence in the market
(she expects prices to double or triple) 
\item Bob would like to lend 1000 USD and get an interest higher than traditional
interest rate offered by banks (let's say 15\% instead of 10\%). He
is either bearish or neutral towards Bitcoin. 
\item Alice transfers her BTC as collateral to a contract, and Bob transfers
his USD to Alice 
\item If Alice pays interest and notional on time (and Btc-price doesn't
render collateral worthless) - she can get her collateral back, otherwise
the loan gets liquidated and collateral is transferred to Bob. 
\end{enumerate}

>>>>

% SJT a couple of questions about these equations
% Q1
% What is the role of the subscript r in \Delta_r
% Q2
% interest rate at t+1 defined from rate at t-1. I'd have expected just one difference, so
% t+1 defined from t, or t defined from t-1.

@@

\noindent
The \emph{spread} parameter here loosely represents the difference between
the average prime 
% SJT explain "prime" here.
rate that the lender expects -- the \emph{benchmark yield} -- and
the rate imposed by the driver - the higher the spread, the higher
the resulting interest rate. The multiplier %effectively 
rescales the interest rate value 
% SJT used value here rather than plot: is that OK?
in order to represent the changes to be made converting between different units
of measurement: how many percentage points 
% SJT percentage points of what?
you would get for a USD-to-kilowatt conversion
and so on.

In the context of ACTUS and other event-based frameworks, 
% SJT - need to explain "event-based" in this context.
there is
one more factor influencing interest rates thorough scaling:

\noindent 
\begin{equation}
interestPayment=interestScalingFactor*interestRate*notional
\end{equation}
\noindent
This scaling is dynamic and loosely adjusts for variance (volatility)
of the asset that the interest rate driver represents.

@@

A counterparty might decide to reinvest profit received as interest
from the %same 
% SJT I think "same" is superfluous here: is that OK?
loan. In the simplest case, this renders as compound
interest. This can be modelled through interest accrual and capitalisation;
% SJT what does "capitalisation" mean?
for instance, contracts from the ACTUS specification accrue interest
between interest payments and can transfer interest to a notional
during interest capitalisation event (IPCL).

Overall, variable interest rates introduce a certain risk for a lender,
thus they can be %are 
subject to hedging. While any instrument that depends
on the same risk factor (interest rate driver) would suffice, the
most popular way to hedge a variable interest rate loan is an interest
rate swap. This instrument allows two (or more) parties to exchange
their incomes - one from a fixed interest rate loan, the other from a variable-rate loan.

@@

Trustless setups, especially ones in the cryptocurrency world, including 
decentralised smart-contracts and exchanges, require no trust between
party and counterparty involved in a contract. In case of a loan,
this literally means that counterparty has zero obligation to pay
the money back, thus rendering the loan useless for a party. Such
risks are usually addressed by introducing collaterals, as in the following scenario. 
\begin{enumerate}
\item Alice would like to borrow 1000 USD 
\item She has Bitcoin assets cost around 1500 USD, which she intends to
hold throughout a year, so Alice has high confidence in the market
(she expects prices to double or triple) 
\item Bob would like to lend 1000 USD and get an interest higher than traditional
interest rate offered by banks (let's say 15\% instead of 10\%). He
is either bearish or neutral towards Bitcoin. 
\item Alice transfers her BTC as collateral to a contract, and Bob transfers
his USD to Alice 
\item If Alice pays the interest and notional on time, and the BTC price does not
render collateral worthless, she can get her collateral back; otherwise
the loan gets liquidated and the collateral is transferred to Bob. 
\end{enumerate}
